LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-01-29 src/ms.tex
data editors won't like that link

A \docsIcon{} symbol in an equation directly links to the relevant online \lw{} documentation for the implementation of that equation, which additionally contains a link to exact code used to reproduce the equation. These derivations are also given in more detail in the \lw{} documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{here}, where we show each of the intervening steps in more detail.

>>>>

A \docsIcon{} symbol in an equation directly links to the relevant online \lw{} documentation for the implementation of that equation, which additionally contains a link to exact code used to reproduce the equation. These derivations are also given in more detail in the \lw{} documentation, where we show each of the intervening steps in more detail.
